### 2022-03-15 manuscript.tex
Update tuba6.svg [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/1e1f9512db5023f364dfc80e35bbd0aad79e8a71.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/1e1f9512db5023f364dfc80e35bbd0aad79e8a71/checks
https://github.com/scherzerthesis/thesis/actions/runs/1987000715

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/6b74dd289e23ad30efba1d526e6f171f6bade1ce/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/6b74dd289e23ad30efba1d526e6f171f6bade1ce}{scherzerthesis/thesis@6b74dd2}
on March 8, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1e1f9512db5023f364dfc80e35bbd0aad79e8a71/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1e1f9512db5023f364dfc80e35bbd0aad79e8a71}{scherzerthesis/thesis@1e1f951}
on March 15, 2022.
